%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     3rd September 2021
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Akhil's Resume
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Akhil}{M}{ {132/47, 3rd cross, Triveni Road, Yeshwanthpur, Bengaluru, India, 560022}\\ +91 9048739634
 | \href{mailto:eminem.akhil17@gmail.com}{eminem.akhil17@gmail.com} | \href{https://www.linkedin.com/in/akhil-m-4a077377/}{Linkedin} | \href{https://github.com/sahridhaya/BitPlease}{GitHub}}

\section{SUMMARY}
\runsubsection{}
\location{Graduate in Mechanical Engineering with proficiency in development, prototyping, analysis, and implementation of algorithms in Image Recognition, Object detection, Data Analysis and an avid robotics enthusiast.}
\begin{tightemize}
    \item Ability to adapt rapidly to new environments and fields of study, such as mathematical modeling, machine learning and its applications across fields like bio-medical and finance.
    \item Socially committed and an active participant in building a technologically aware and active community of youngsters, thereby empowering them to solve the vital challenges of society through technology and alternative education.  
\end{tightemize}

\section{EDUCATION}

\runsubsection{Bachelor's in Mechanical Engineering}
\descript{| \textbf{\href{http://www.gecbh.ac.in/}{GOVERNMENT ENGINEERING COLLEGE BARTON HILL}} THIRUVANANTHAPURAM, KERALA, INDIA }
\location{8 semester program with 120 cumulative credits}
\location{Overall GPA: 9.33/10 | Graduation Date: July 2021 }
\sectionsep

\runsubsection{School}
\descript{| Kendriya Vidyalaya SAP, PEROORKADA, KERALA}
\location{March 2007 – March 2017 | CBSE PERCENTAGE: 92}
\location{High School and Senior Secondary}
\sectionsep

%\section{Projects}
%\runsubsection{Student Projects}
%\begin{tightemize}
%\item Course MACHINE ELEMENTS II: "Design a Reduction Gearbox"
%\item Course MECHANICAL ENGINEERING LABORATORY: "Heat exchangers", "Boilers", "Metallic Materials", "Data analysis"
%\end{tightemize}
%\sectionsep


\section{work experience}

\runsubsection{Research Assistant}
\descript{| \textbf{\href{https://iisc.ac.in/}{IISc}} , BENGALURU, INDIA}
\location{August 2021 - Present | ML \& AI Project Assistant at \href{https://labs.dese.iisc.ac.in/beeslab/}{BEES LAB, DESE}}
Currently working alongside PhD. scholars with the guidance of Dr. Hardik J. Pandya on projects with ML or AI aspects in Biomedical domain. Developing and optimizing algorithms for image recognition, deep learning and data analysis. 
\sectionsep

\runsubsection{Internship}
\descript{| \textbf{\href{https://iisc.ac.in/}{IISc}} , BENGALURU, INDIA}
\location{June 2021 - August 2021 | Data Analysis Intern}
The tasks I was assigned entails data cleanup, analysis and interpretation for the assistance of research students.
Indicative examples of such projects include:
\begin{tightemize}
\item Cleaning up of data with over thousands of rows and Visualizing with plots and charts using Microsoft Excel
\item Automating cleaning up and visualization using Python programming with tools such as Pandas, Numpy and Matplotlib
\end{tightemize}
\sectionsep

\runsubsection{Internship}
\descript{| \textbf{{Dot Product}} , KERALA, INDIA}
\location{January 2021 - March 2021 | Data Analysis Intern}
\sectionsep

\runsubsection{Position Held}
\descript{| \textbf{{Bartonoidz, ISTE}} , KERALA, INDIA}
\location{May 2020 - June 2021 | Chairman at Bartonoidz Robotics Club}
Chairman at Bartonoidz, the robotics club of GOVERNMENT ENGINEERING COLLEGE BARTON HILL under Indian Society for Technical Education(ISTE)
\sectionsep

\section{Publications}
\location{Processing and Characterization of 3D‑Printed Inconel‑718 Component through Laser Powder Bed Fusion Route for High‑Temperature Space Application}
\textbf{JOURNAL: }
{Indian National Academy of Engineering(INAE)}

\href{https://doi.org/10.1007/s41403-020-00196-6}{https://doi.org/10.1007/s41403-020-00196-6}
\sectionsep

\section{skills}
\runsubsection{Language Skills}
\location{}
\begin{tightemize}
\item English: Full Professional Proficiency 
\item Hindi: Limited Working Proficiency 
\item Malayalam: Native Speaker
\item German: Elementary Proficiency 
\end{tightemize}
\sectionsep


\runsubsection{Software Skills}
\location{}
C++ \textbullet{}   PYTHON \textbullet{}  Microsoft EXCEL/PPT/WORD \textbullet{} R \textbullet{} AUTOCAD \textbullet{} Adobe Photoshop/Premier Pro \textbullet{} TABLEU 
\sectionsep

\runsubsection{Professional Skills}
\location{}
Critical Thinking \textbullet{} Teamwork \textbullet{} Problem Solving
\sectionsep

\runsubsection{Driving Licence}
\location{}
\begin{tightemize}
\item Indian Driving License Category LMV 
\end{tightemize}
\sectionsep

\section{Projects}
\location{Obstacle avoiding Robot}
\begin{tightemize}
    \item Obstacle Avoiding Robot is an intelligent device which can automatically sense the obstacle in front of it and avoid them by turning itself in another direction. The said project was completed using an Arduino and Ultrasound sensors. 
\end{tightemize}
\location{Quadriplegic Cap}
\begin{tightemize}
    \item Quadriplegia, or tetraplegia, is a condition where all four limbs experience paralysis. Quadriplegics often have experienced severe trauma. A cap was developed for assisting said patients for navigating on a computer screen. It was completed using an Accelerometer and by using a Microcontroller.
\end{tightemize}
\location{Gas Sensing Grenade}
\begin{tightemize}
    \item Gas sensing grenade( GSG ) can be thrown inside the building with fire or other dangerous conditions. The module consist of an MQ2 gas sensor, a microcontroller and a 433MHz transmitter, and 9v battery. The MQ2 gas sensor can sense Methane, LPG, Butane and Smoke. It senses the gas in PPM values and will be monitored by the microcontroller. This values are then transmitted back to the receiver.
\end{tightemize}
\location{Unmanned Underwater Vehicle (DRDO)}
\begin{tightemize}
    \item Submitted a proposal for an Unmanned Underwater Vehicle as part of DRDO(Defence Research and Development Organisation) Robotics and Unmanned Systems Exposition event.
\end{tightemize}
\location{Paper Pen Vending Machine}
\begin{tightemize}
    \item A smart paper pen vending machine was designed and developed. This project was developed in order to address the issue of plastic pens as a waste in the college campus environment. A paper pen is given in return when 3 plastic pens are deposited into the machine. The machine was completed using a Raspberry pi, pi cam and various sensors. Machine learning and image recognition was used for this.
\end{tightemize}
\sectionsep

\section{Achievements}
\location{Robothon 4.0 - Runners Up}
    ROBOTHON 4.0 was a 3-day National robotics hackathon conducted by IEEE College of Engineering Chengannur Students Branch.

\location{Hacksquad 2.0 - Winner}
    One day national hardware and software hackathon organized by IET SB, College of Engineering Trivandrum as part of their technical fest DRISHTI

\location{Arduino Buzz(2019) - Winner}
    One day Arduino based hackathon conducted by LBS institute of Technology for Women(LBSITW), Trivandrum

\location{Arduino Makeathon - Winner}
    One day Arduino based hackathon conducted by Sree Chitra Thirunal College of Engineering(SCTCE), Pappanamcode, Trivandrum
\sectionsep

\section{Certifications}
\location{\href{https://fossee.in/fellowship/2019}{FOSSEE IIT Bombay Summer Fellowship 2019 - } \href{https://static.fossee.in/fossee/fellowship2019/FOSSEE-Fellowship-reports-2019/R/R_SolidWasteManagementSystem_Thiruvananthapuram_Fellowship2019.pdf}{Report}}
\location{\href{https://coursera.org/share/bde6ea7e89e38dc2128ff8cae2ad2dc8}{Architecting with Google Compute Engine by Google Cloud on Coursera}}
\location{\href{https://coursera.org/share/1bdd6e55dcd2f71c4636e6aa03b90655}{IBM Applied AI by IBM on Coursera}}
\location{\href{https://coursera.org/share/fdf77307df253e918f1cfa6535e2f001}{IBM AI Engineering by IBM on Coursera}}
    
\sectionsep

\section{Interests}
Guitar\textbullet{} Programming\textbullet{} Tech\textbullet{} Gaming \textbullet{} Photography 
\sectionsep
%\section{Languages}
%\begin{minipage}[t]{.6\textwidth}
%\subsection{Programming}
%\location{Over 5000 lines:}
%Java \textbullet{}   Shell \textbullet{} JavaScript \textbullet{} Matlab \textbullet{}
%OCaml \textbullet{} Python \textbullet{} Rails \textbullet{} \LaTeX\ \\ 
%\location{Over 1000 lines:}
%C \textbullet{} C++ \textbullet{} CSS \textbullet{} PHP \textbullet{} Assembly \\
%\location{Familiar:}
%AS3 \textbullet{} iOS \textbullet{} Android \textbullet{} MySQL
%\sectionsep
%\end{minipage}
%\hfill
%\begin{minipage}[t]{.35\textwidth}
%\subsection{Spoken \& Written}
%\location{Native fluency:} English, Spanish\\
%\location{Reading fluency:} Chinese, Japanese\\
%\end{minipage}

\end{document}  \documentclass[]{article}